Carbonate chemistry at Ny-Ålesund

### 2021-12-09 awipev-CO2.Rmd
adding quality plot for seaFET measurements + group_by(datetime) instead of date in discrete df+ adding hour column in d_all

if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")
if (!require("readxl")) install.packages("readxl")
library("readxl")
if (!require("oce")) install.packages("oce")
library(oce)

@@

d_all <- d_hour %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & depth <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & depth <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & depth <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 10, NA)
          )
        )
      )
    ),
    depth_group_philipp = ifelse( # create new variable depth
      depth <= 2,
      1,
      ifelse(
        depth > 2 & depth <= 4,
        3,
        ifelse(
          depth > 4 & depth <= 6,
          5,
          ifelse(
            depth > 6 & depth <= 8,
            7,
            ifelse(depth > 8, 10, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    temp_insitu_ctd_1m,
    temp_insitu_ctd_3m,
    temp_insitu_ctd_5m,
    temp_insitu_ctd_7m,
    temp_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
rm(d_hour)

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all %>%
                 dplyr::select(
                   c(closest_datetime,
                     sal_fb,
                     temp_fb,
                     temp_mix,
                     temp_mix_interp,
                     sal_mix,
                     sal_mix_interp,
                     temp_insitu_11m,
                     temp_insitu_ctd,
                     temp_sf,
                     depth
                   )
                 ), by = "closest_datetime") %>% 
  dplyr::select(-closest_datetime)

@@

#put back the right column name for the following script
pH_durafet_mean$ph_s_dur_temp_fb <- pH_durafet_mean$ph_s_dur_temp_fb_mean
pH_seafet_mean$ph_s_sf_temp_insi <- pH_seafet_mean$ph_s_sf_temp_insi_mean
#  make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  dplyr::group_by(date) %>%
  dplyr::summarize(
    datetime = mean(datetime, na.rm = TRUE),
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_mix = mean(sal_mix, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    #qflag_at = mean(qflag_at, na.rm = TRUE), # already dealt with above
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE),
    #qflag_ct = mean(qflag_ct, na.rm = TRUE)  # already dealt with above
    temp_mix = mean(temp_mix, na.rm = TRUE),
    temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE)
  )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
discrete <- left_join(discrete, pH_durafet_mean, by='datetime')

@@

# pH calculated (at and ct) at Ferrybox sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
discrete_no_na$ph_calc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
discrete_no_na$pco2_calc_fb <- carb$pCO2

@@

# bind new calibrated pH data to the seafet data set.
names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")

##########  Despike() ###########
d_all <- d_all %>%   
  dplyr::mutate(pHint_tot_sf = oce::despike(seafet_calib$pHint_tot_sf, reference= "median", n=1, k=5000, replace="NA"),
                pHext_tot_sf = oce::despike(seafet_calib$pHext_tot_sf, reference= "median", n=1, k=5000, replace="NA")
  )

@@

dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#CCCCCC") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-3, 9)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
rm(seafet_depth_xts)
```

@@

```{r seaFET quality control pH, echo=FALSE, warning = FALSE, message = FALSE, out.width='100%'}
#Offset between seafet pH and spec pH (Fig. 2 Kapsenberg et al.)

ph_sf <- d_all%>%
  mutate( diff_pH = ph_s_sf_temp_insi - pHint_tot_sf)
average_offset <- mean(abs(ph_sf$diff_pH), na.rm=TRUE)

offset_xts <- dplyr::select(ph_sf%>%dplyr::filter(!is.na(diff_pH)), datetime, diff_pH)
offset_xts <- as.xts(offset_xts, order.by=offset_xts$datetime)

dygraph(offset_xts, ylab = "") %>%
dySeries("diff_pH", drawPoints = TRUE, pointSize=3, label = "delta pHINT", color="green")%>%
    dyLimit(0,strokePattern = "dashed", color = "black") %>% 
  dyLimit(-0.02,strokePattern = "dashed", color = "red") %>% 
    dyLimit(0.02,strokePattern = "dashed", color = "red") %>% 
 # dyAxis("y",valueRange = c(-0.04, 0.04))%>%
  dyAxis("x",valueRange = c(as.POSIXct("2021-09-28"), as.POSIXct("2021-10-19")
))%>%
dyOptions(
    drawGrid = TRUE,
    strokeWidth= 0,
    drawPoints = TRUE,
    useDataTimezone = TRUE,
    digitsAfterDecimal = 4) %>%
  dyRangeSelector(height = 30)
```

>>>>

library("RColorBrewer")
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")
if (!require("readxl")) install.packages("readxl")
library("readxl")
if (!require("oce")) install.packages("oce")
library(oce)

@@

d_all <- d_hour %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & depth <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & depth <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & depth <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 10, NA)
          )
        )
      )
    ),
    depth_group_philipp = ifelse( # create new variable depth
      depth <= 2,
      1,
      ifelse(
        depth > 2 & depth <= 4,
        3,
        ifelse(
          depth > 4 & depth <= 6,
          5,
          ifelse(
            depth > 6 & depth <= 8,
            7,
            ifelse(depth > 8, 10, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    temp_insitu_ctd_1m,
    temp_insitu_ctd_3m,
    temp_insitu_ctd_5m,
    temp_insitu_ctd_7m,
    temp_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) ,
                hour = lubridate::hour(d_hour$datetime)# abbreviated months
  )
rm(d_hour)

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime

d <- left_join(d, d_all %>%
                 dplyr::select(
                   c(closest_datetime,
                     hour,
                     sal_fb,
                     temp_fb,
                     temp_mix,
                     temp_mix_interp,
                     sal_mix,
                     sal_mix_interp,
                     temp_insitu_11m,
                     temp_insitu_ctd,
                     temp_sf,
                     depth
                   )
                 ), by = "closest_datetime") %>% 
  dplyr::select(-closest_datetime)

@@

#put back the right column name for the following script
pH_durafet_mean$ph_s_dur_temp_fb <- pH_durafet_mean$ph_s_dur_temp_fb_mean
pH_seafet_mean$ph_s_sf_temp_insi <- pH_seafet_mean$ph_s_sf_temp_insi_mean

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  group_by(datetime) %>%
#dplyr::select( datetime, date,hour,sal_fb,sal_mix_interp ,sal_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_mix,temp_mix_interp,temp_insitu_11m) %>%
  summarise(datetime = mean(datetime, na.rm = TRUE),
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_mix = mean(sal_mix, na.rm = TRUE),
    sal_mix_interp = mean(sal_mix_interp, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
     temp_mix = mean(temp_mix, na.rm = TRUE),
    temp_mix_interp = mean(temp_mix_interp, na.rm = TRUE),
        temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'

# library("RColorBrewer")
# d_xts <- dplyr::select(discrete, datetime, sal_fb, sal_mix,temp_fb,temp_mix,temp_insitu_11m, at_mean_interp,at,ct_mean_interp,ct)
# d_xts <- as.xts(d_xts, order.by = d_xts$datetime)
# dygraph(d_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
#             dySeries("sal_mix", color = brewer.pal(n=9, name = "Paired")[1], strokeWidth = 1, pointSize = 4, label = "sal_mix") %>%
#             dySeries("sal_fb", color = brewer.pal(n=9, name = "Paired")[2], strokeWidth = 1, pointSize = 2, label = "sal_fb") %>%
#    dySeries("temp_mix", color = brewer.pal(n=9, name = "Paired")[3], strokeWidth = 1, pointSize = 4, label = "temp_mix") %>%
#    dySeries("temp_fb", color = brewer.pal(n=9, name = "Paired")[4], strokeWidth = 1, pointSize = 2, label = "temp_fb") %>%
#    dySeries("temp_insitu_11m", color = brewer.pal(n=9, name = "Paired")[5], strokeWidth = 1, pointSize = 2, label = "temp_insitu_11m") %>%
#     dySeries(axis="y2", "at_mean_interp", color = brewer.pal(n=9, name = "Paired")[6], strokeWidth = 1, pointSize = 4, label = "at_mean_interp") %>%
#    dySeries(axis="y2","ct_mean_interp", color =brewer.pal(n=9, name = "Paired")[7], strokeWidth = 1, pointSize = 4, label = "ct_mean_interp") %>%
#  dySeries(axis="y2","at", color = brewer.pal(n=9, name = "Paired")[8], strokeWidth = 1, pointSize = 2, label = "at") %>%
#    dySeries(axis="y2","ct", color =brewer.pal(n=9, name = "Paired")[9], strokeWidth = 1, pointSize = 2, label = "ct") %>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
#       dyOptions( drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
#     dyLegend(show = "follow")   %>%
#    # dyAxis("y",valueRange = c(30, 37)) %>%
#       dyRangeSelector(height = 30, dateWindow= NULL)

discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
discrete <- left_join(discrete, pH_durafet_mean, by='datetime')

@@

# pH calculated (at and ct) at Ferrybox sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at_mean_interp*1e-6, discrete_no_na$ct_mean_interp*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
discrete_no_na$ph_calc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
discrete_no_na$pco2_calc_fb <- carb$pCO2

@@

# bind new calibrated pH data to the seafet data set.
names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")
##########  Despike() ###########
d_all <- d_all %>%   
  dplyr::mutate(pHint_tot_sf = oce::despike(seafet_calib$pHint_tot_sf, reference= "median", n=1, k=5000, replace="NA"),
                pHext_tot_sf = oce::despike(seafet_calib$pHext_tot_sf, reference= "median", n=1, k=5000, replace="NA")
  )

@@

dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#CCCCCC") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-3, 9)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= c("2017-08-10 00:00:00","2021-01-20 23:00:00"))
rm(seafet_depth_xts)
```

@@

```{r seaFET quality control pH 1, echo=FALSE, warning = FALSE, message = FALSE, out.width='100%'}
#Offset between seafet pH and spec pH (Fig. 2 Kapsenberg et al.)
ph_sf <- d_all%>%
  dplyr::select(datetime, ph_s_sf_temp_insi,pHint_tot_sf,pHext_tot_sf)%>%
    dplyr::mutate( diff_spec_sf = ph_s_sf_temp_insi - pHint_tot_sf,
                   diff_sf_int_ext = pHint_tot_sf -pHext_tot_sf )
average_offset <- mean(ph_sf$diff_spec_sf, na.rm=TRUE, digits=4)

offset_xts <- select(ph_sf, datetime, diff_spec_sf)
offset_xts <- as.xts(offset_xts, order.by=offset_xts$datetime)

dygraph(offset_xts, main = "delta spectro - INT calibrated seaFET") %>%
dySeries("diff_spec_sf", drawPoints = TRUE, pointSize=4, label = "Delta", color="green")%>%
    dyLimit(0,strokePattern = "solid", color = "black") %>% 
  dyLimit(-0.02,strokePattern = "dashed", color = "red") %>% 
    dyLimit(0.02,strokePattern = "dashed", color = "red") %>% 
  dyAxis("y",valueRange = c(-0.08, 0.14))%>%
    dyLegend(show = "follow")   %>%
 # dyAxis("x",valueRange = c(as.POSIXct("2021-09-28"), as.POSIXct("2021-10-19")))%>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
dyOptions(
    drawGrid = TRUE,
    strokeWidth= 0,
    drawPoints = TRUE,
    useDataTimezone = TRUE,
    digitsAfterDecimal = 4) %>%
  dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
```

- pH INT - pH EXT was plotted here.

```{r seaFET quality control pH 2, echo=FALSE, warning = FALSE, message = FALSE, out.width='100%'}
                                                                                                                                                                                       ## INT -EXT
delta_xts <- dplyr::select(ph_sf,datetime, diff_sf_int_ext, pHext_tot_sf, pHint_tot_sf)
delta_xts <- as.xts(delta_xts, order.by=delta_xts$datetime)
dygraph(delta_xts, main = "delta pHINT - pH EXT") %>%
  dySeries(axis ="y2","pHext_tot_sf", drawPoints = TRUE, pointSize=3, label = "pH EXT", color="red")%>%
dySeries(axis ="y2","pHint_tot_sf", drawPoints = TRUE, pointSize=2, label = "pH INT", color="blue")%>%
  dySeries( "diff_sf_int_ext", drawPoints = TRUE, pointSize=2, label = "Delta", color="grey")%>%
    dyLegend(show = "follow")   %>%
      dyLimit(0,strokePattern = "solid", color = "black") %>% 
 dyAxis("y",valueRange = c(-0.3,0.3))%>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
dyOptions(
    drawGrid = TRUE,
    strokeWidth= 0,
    drawPoints = TRUE,
    useDataTimezone = TRUE,
    digitsAfterDecimal = 4) %>%
  dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
